---
title: "TDI Daily Max"
author: "Molly Williams"
date: "3/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Load packages and data

```{r}

library(here)
library(tidyverse)
library(lubridate)
library(janitor)
library(KernSmooth)


# import data and add columns for water year, month and day (Oct 1 = 1, Nov 1 = 32 etc through 365-66 for each year)
#rcp45 <- read_csv("tdi/RCP45_dailymax.csv") %>% 
#  mutate(water_year = ifelse(Month>9, Year+1, Year)) %>% 
#  mutate(water_month = ifelse(Month<10, Month+3, ifelse(Month>9, Month-9, Month))) %>% 
#  mutate(date_combine = make_datetime(water_year, water_month, Day)) %>% 
#  mutate(water_day = yday(date_combine)) %>%  # extract day of year from combined date

### some discrepancies here because of mismatched days/months (e.g. for 1981 water day 60 is duplicated); check dupes:
# rcp_test <- rcp45 %>% filter(water_year == 1985)

# dupes5 <- get_dupes(rcp_test, water_day) %>% 
#  select(Year, Month, Day, water_year, water_month, water_day, dupe_count)


### Doesn't seem like there's a good way to address this issue without over-manipulating the dates, so going to try a different method. It's not the most elegant, but it works:

leap_years <- c(1980, 1984, 1988, 1992, 1996, 2000, 2004, 2008, 2012, 2016, 2020, 2024, 2028, 2032, 2036, 2040, 2044, 2048, 2052, 2056, 2060, 2064, 2068, 2072, 2076, 2080, 2084, 2088, 2092, 2096)

# Create water day column for data from leap years
rcp45_1 <- read_csv("RCP45_dailymax.csv") %>% 
  mutate(water_year = ifelse(Month>9, Year+1, Year)) %>% 
  mutate(water_month = ifelse(Month<10, Month+3, ifelse(Month>9, Month-9, Month))) %>% 
  filter(water_year %in% leap_years) %>%
  filter(water_year != 1980) %>% # keeping only complete data years
  mutate(water_day = as.numeric(rep(1:366, 29)))

# Create water day column for data from non-leap years
rcp45_2 <- read_csv("RCP45_dailymax.csv") %>% 
  mutate(water_year = ifelse(Month>9, Year+1, Year)) %>% 
  mutate(water_month = ifelse(Month<10, Month+3, ifelse(Month>9, Month-9, Month))) %>% 
  filter(!water_year %in% leap_years) %>% 
  filter(water_year != 1980) %>% # keeping only complete data years
  mutate(water_day = as.numeric(rep(1:365, 90)))

# Combine into a single data frame
rcp45 <- rbind(rcp45_1, rcp45_2)



## Repeat for RCP 8.5 data: 
# Create water day column for data from leap years
rcp85_1 <- read_csv("RCP85_dailymax.csv") %>% 
  mutate(water_year = ifelse(Month>9, Year+1, Year)) %>% 
  mutate(water_month = ifelse(Month<10, Month+3, ifelse(Month>9, Month-9, Month))) %>% 
  filter(water_year %in% leap_years) %>%
  filter(water_year != 1980) %>% # keeping only complete data years
  mutate(water_day = as.numeric(rep(1:366, 29)))

# Create water day column for data from non-leap years
rcp85_2 <- read_csv("RCP85_dailymax.csv") %>% 
  mutate(water_year = ifelse(Month>9, Year+1, Year)) %>% 
  mutate(water_month = ifelse(Month<10, Month+3, ifelse(Month>9, Month-9, Month))) %>% 
  filter(!water_year %in% leap_years) %>% 
  filter(water_year != 1980) %>% # keeping only complete data years
  mutate(water_day = as.numeric(rep(1:365, 90))) 

# Combine into a single data frame
rcp85 <- rbind(rcp85_1, rcp85_2)

```



# Isolate 10 largest flow days from each year and model

```{r}

# Convert to long/tidy data
rcp45_long <- rcp45 %>% 
  select(-Year, -Month, -Day) %>% 
  pivot_longer(-c(water_year, water_month, water_day), names_to = "model", values_to = "flow") %>% 
  mutate(rcp = 4.5)

rcp85_long <- rcp85 %>% 
  select(-Year, -Month, -Day) %>% 
  pivot_longer(-c(water_year, water_month, water_day), names_to = "model", values_to = "flow") %>% 
  mutate(rcp = 8.5)


# Combine all data into single df

all_daily_flows <- rbind(rcp45_long, rcp85_long)


# Find top 10 flow values for each model and each year
top10_annual_flows <- all_daily_flows %>% 
  group_by(water_year, model, rcp) %>% 
  top_n(10, flow) %>% 
  write_csv("tdi/top10_annual_flows.csv")

# all the top 10 flows are within a consecutive streak 


# If top 10 flows fall within consecutive streak(s) of water_days, take only the highest value from each streak

group_by(rcp, model, water_year) %>% 
function() that asks:
#  do water_day values fall within consecutive streak(s)?
#  if yes, retain only max value
  
# create a for loop for this? save all of the diff models in csvs , then re-import perform the operations on them


  
  
```




# Top 10 flows for each model/scenario (20 total)


```{r}
# Isolate data for ten highest flows from each model/RCP scenario

## Create function
top10 <- function(x, y) { # Inputs/parameters: x = df name, y = model name
  model_rcp <- x %>% 
  select(water_year, water_month, water_day, flow = y) %>%
  group_by(water_year) %>% 
  top_n(10, flow) %>% 
  arrange(water_year, water_day)

}

## Apply function to create new dfs for each model/RCP scenario

access_45 <- top10(rcp45, "ACCESS1-0")
access_85 <- top10(rcp85, "ACCESS1-0")

CCSM4_45 <- top10(rcp45, "CCSM4")
CCSM4_85 <- top10(rcp85, "CCSM4")

CESM1_45 <- top10(rcp45, "CESM1-BGC")
CESM1_85 <- top10(rcp85, "CESM1-BGC")

CMCC_45 <- top10(rcp45, "CMCC-CMS")
CMCC_85 <- top10(rcp85, "CMCC-CMS")

CMCC_45 <- top10(rcp45, "CMCC-CMS")
CMCC_85 <- top10(rcp85, "CMCC-CMS")

CNRM_45 <- top10(rcp45, "CNRM-CM5")
CNRM_85 <- top10(rcp85, "CNRM-CM5")

CanESM2_45 <- top10(rcp45, "CanESM2")
CanESM2_85 <- top10(rcp85, "CanESM2")

GFDL_45 <- top10(rcp45, "GFDL-CM3")
GFDL_85 <- top10(rcp85, "GFDL-CM3")

HCC_45 <- top10(rcp45, "HadGEM2-CC")
HCC_85 <- top10(rcp85, "HadGEM2-CC")

HES_45 <- top10(rcp45, "HadGEM2-ES")
HES_85 <- top10(rcp85, "HadGEM2-ES")

MIROC5_45 <- top10(rcp45, "MIROC5")
MIROC5_85 <- top10(rcp85, "MIROC5")


```


# Select maximum values from individual storms 


## Create functions to apply to each model and scenario 
```{r}

# Determine length of consecutive sequence of water_days and bind to flow data

seqle <- function(x,incr=1) { 
  if(!is.numeric(x)) x <- as.numeric(x) 
  n <- length(x)  
  y <- x[-1L] != x[-n] + incr 
  i <- c(which(y|is.na(y)),n) 
  list(lengths = diff(c(0L,i)),
       values = x[head(c(0L,i)+1L,-1L)]) 
} 

consec_count <- function(x) { # x = model+RCP data frame
  df <- x
  result <- seqle(df$water_day)
  consec_length <- data.frame(rep = rep(result$lengths, result$lengths))
  bind_cols(x, consec_length)
}

# Find maximum flow value within consecutive water_day period
consec_max <- function(x) {
  model_rcp <- x %>% 
  group_by(water_year, water_month, rep) %>% 
  summarize(flow = max(flow)) %>% 
  ungroup()
}


```


## Apply functions to all individual data frames for each model/scenario

```{r}

# Would love to do this in a loop but can't figure it out...

# dfs <- list(access_45, access_85)

# for (i in seq_along(dfs)) {
#  dfs[[i]] <- consec_count(df[[i]]) }


access_45_max <- access_45 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "ACCESS1-0") %>% 
  mutate(rcp = "4.5")

access_45_max <- left_join(access_45_max, access_45, by = c("flow", "water_year", "water_month")) # retain water_day data


access_85_max <- access_85 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "ACCESS1-0") %>% 
  mutate(rcp = "8.5")

access_85_max <- left_join(access_85_max, access_85, by = c("flow", "water_year", "water_month")) # retain water_day data



CCSM4_45_max <- CCSM4_45 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "CCSM4") %>% 
  mutate(rcp = "4.5")

CCSM4_45_max <- left_join(CCSM4_45_max, CCSM4_45, by = c("flow", "water_year", "water_month")) # retain water_day data


CCSM4_85_max <- CCSM4_85 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "CCSM4") %>% 
  mutate(rcp = "8.5")

CCSM4_85_max <- left_join(CCSM4_85_max, CCSM4_85, by = c("flow", "water_year", "water_month")) # retain water_day data


CESM1_45_max <- CESM1_45 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "CESM1") %>% 
  mutate(rcp = "4.5")

CESM1_45_max <- left_join(CESM1_45_max, CESM1_45, by = c("flow", "water_year", "water_month")) # retain water_day data


CESM1_85_max <- CESM1_85 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "CESM1") %>% 
  mutate(rcp = "8.5")

CESM1_85_max <- left_join(CESM1_85_max, CESM1_85, by = c("flow", "water_year", "water_month")) # retain water_day data


CMCC_45_max <- CMCC_45 %>% 
  consec_count() %>% 
  consec_max( ) %>% 
  mutate(model = "CMCC") %>% 
  mutate(rcp = "4.5")

CMCC_45_max <- left_join(CMCC_45_max, CMCC_45, by = c("flow", "water_year", "water_month")) # retain water_day data


CMCC_85_max <- CMCC_85 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "CMCC") %>% 
  mutate(rcp = "8.5") 

CMCC_85_max <- left_join(CMCC_85_max, CMCC_85, by = c("flow", "water_year", "water_month")) # retain water_day data




CNRM_45_max <- CNRM_45 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "CNRM") %>% 
  mutate(rcp = "4.5")  

CNRM_45_max <- left_join(CNRM_45_max, CNRM_45, by = c("flow", "water_year", "water_month")) # retain water_day data


CNRM_85_max <- CNRM_85 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "CNRM") %>% 
  mutate(rcp = "8.5")
  
CNRM_85_max <- left_join(CNRM_85_max, CNRM_85, by = c("flow", "water_year", "water_month")) # retain water_day data


CanESM2_45_max <- CanESM2_45 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "CanESM2") %>% 
  mutate(rcp = "4.5")

CanESM2_45_max <- left_join(CanESM2_45_max, CanESM2_45, by = c("flow", "water_year", "water_month")) # retain water_day data


CanESM2_85_max <- CanESM2_85 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "CanESM2") %>% 
  mutate(rcp = "8.5")
  
CanESM2_85_max <- left_join(CanESM2_85_max, CanESM2_85, by = c("flow", "water_year", "water_month")) # retain water_day data

  

GFDL_45_max <- GFDL_45 %>%  
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "GFDL") %>% 
  mutate(rcp = "4.5") 

GFDL_45_max <- left_join(GFDL_45_max, GFDL_45, by = c("flow", "water_year", "water_month")) # retain water_day data


GFDL_85_max <- GFDL_85 %>%  
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "GFDL") %>% 
  mutate(rcp = "8.5")

GFDL_85_max <- left_join(GFDL_85_max, GFDL_85, by = c("flow", "water_year", "water_month")) # retain water_day data


HCC_45_max <- HCC_45 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "HadGEM2-CC") %>% 
  mutate(rcp = "4.5") 

HCC_45_max <- left_join(HCC_45_max, HCC_45, by = c("flow", "water_year", "water_month")) # retain water_day data


HCC_85_max <- HCC_85 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "HadGEM2-CC") %>% 
  mutate(rcp = "8.5")

HCC_85_max <- left_join(HCC_85_max, HCC_85, by = c("flow", "water_year", "water_month")) # retain water_day data


HES_45_max <- HES_45 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "HadGEM2-ES") %>% 
  mutate(rcp = "4.5") 

HES_45_max <- left_join(HES_45_max, HES_45, by = c("flow", "water_year", "water_month")) # retain water_day data


HES_85_max <- HES_85 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "HadGEM2-ES") %>% 
  mutate(rcp = "8.5") 

HES_85_max <- left_join(HES_85_max, HES_85, by = c("flow", "water_year", "water_month")) # retain water_day data



MIROC5_45_max <- MIROC5_45 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "MIROC5") %>% 
  mutate(rcp = "4.5")

MIROC5_45_max <- left_join(MIROC5_45_max, MIROC5_45, by = c("flow", "water_year", "water_month")) # retain water_day data


MIROC5_85_max <- MIROC5_85 %>% 
  consec_count() %>% 
  consec_max() %>% 
  mutate(model = "MIROC5") %>% 
  mutate(rcp = "8.5")

MIROC5_85_max <- left_join(MIROC5_85_max, MIROC5_85, by = c("flow", "water_year", "water_month")) # retain water_day data


max_tdi_all <- rbind(access_45_max, access_85_max, CCSM4_45_max, CCSM4_85_max, CESM1_45_max, CESM1_85_max, CMCC_45_max, CMCC_85_max, CNRM_45_max, CNRM_85_max, CanESM2_45_max, CanESM2_85_max, GFDL_45_max, GFDL_85_max, HCC_45_max, HCC_85_max, HES_45_max, HES_85_max, MIROC5_45_max, MIROC5_85_max)





```


# Analyze distribution of months through different time period

## Filter and organize data + quick look
```{r}


daily_hist <- max_tdi_all %>% 
  filter(water_year < 2010) %>% 
  mutate(scenario = "RCP 4.5 & 8.5 1995")

hist(daily_hist$water_day) # quick look

daily_rcp45_2070 <- max_tdi_all %>% 
  filter(rcp == 4.5) %>% 
  filter(water_year > 2054) %>% 
  filter(water_year < 2085) %>% 
  mutate(scenario = "RCP 4.5 2070")


daily_rcp45_2085 <- max_tdi_all %>% 
  filter(rcp == 4.5) %>% 
  filter(water_year > 2069) %>% 
  mutate(scenario = "RCP 4.5 2085")


daily_rcp85_2050 <- max_tdi_all %>% 
  filter(rcp == 8.5) %>% 
  filter(water_year > 2034) %>% 
  filter(water_year < 2065) %>% 
  mutate(scenario = "RCP 8.5 2050")


daily_rcp85_2070 <- max_tdi_all %>% 
  filter(rcp == 8.5) %>% 
  filter(water_year > 2054) %>% 
  filter(water_year < 2085) %>% 
  mutate(scenario = "RCP 8.5 2070")


daily_rcp85_2085 <- max_tdi_all %>% 
  filter(rcp == 8.5) %>% 
  filter(water_year > 2069) %>% 
  mutate(scenario = "RCP 8.5 2085")

  

```



## Visualize distributions with histograms

```{r}


daily_hist_plot <- daily_hist %>%
  group_by(water_day) %>% 
  tally() %>%
  ggplot(aes(water_day, n)) + 
  geom_col(fill = "gray") +
  ylim(0, 25) +
  xlab("Water Day (1 = Oct 1)") +
  ylab("Occurrences") +
  ggtitle(label = "Annual distribution of TDI maxima", 
       subtitle = "Daily data, RCP 4.5 and 8.5, 1980-2009") +
  theme_bw() +
  ggsave("tdi/figures/daily/historical.png")

daily_hist_plot


daily_rcp45_2070_plot <- daily_rcp45_2070 %>%
  group_by(water_day) %>% 
  tally() %>%
  ggplot(aes(water_day, n)) + 
  geom_col(fill = "gray") +
  ylim(0, 25) +
  xlab("Water Day (1 = Oct 1") +
  ylab("Occurrences") +
  ggtitle(label = "Annual distribution of tidal maxima",
  subtitle = "Daily data, RCP 4.5, 2055-2084") +
  theme_bw() +
  ggsave(here("tdi/figures/daily/rcp45_2070_daily.png"))


daily_rcp45_2085_plot <- daily_rcp45_2085 %>%
  group_by(water_day) %>% 
  tally() %>%
  ggplot(aes(water_day, n)) + 
  geom_col(fill = "gray") +
  ylim(0, 25) +
  xlab("Water Day (1 = Oct 1") +
  ylab("Occurrences") +
  ggtitle(label = "Annual distribution of tidal maxima",
  subtitle = "Daily data, RCP 4.5, 2070-2099") +
  theme_bw() +
  ggsave(here("tdi/figures/daily/rcp45_2085_daily.png"))


daily_rcp85_2050_plot <- daily_rcp85_2050 %>%
  group_by(water_day) %>% 
  tally() %>%
  ggplot(aes(water_day, n)) + 
  geom_col(fill = "gray") +
  ylim(0, 25) +
  xlab("Water Day (1 = Oct 1") +
  ylab("Occurrences") +  
  ggtitle(label = "Annual distribution of tidal maxima",
  subtitle = "Daily data, RCP 8.5, 2035-2064") +
  theme_bw() +
  ggsave(here("tdi/figures/daily/rcp85_2050_daily.png"))



daily_rcp85_2070_plot <- daily_rcp85_2070 %>%
  group_by(water_day) %>% 
  tally() %>%
  ggplot(aes(water_day, n)) + 
  geom_col(fill = "gray") +
  ylim(0, 25) +
  xlab("Water Day (1 = Oct 1") +
  ylab("Occurrences") +
  ggtitle(label = "Annual distribution of tidal maxima",
  subtitle = "Daily data, RCP 8.5, 2055-2084") +
  theme_bw() +
  ggsave(here("tdi/figures/daily/rcp85_2070_daily.png"))


daily_rcp85_2085_plot <- daily_rcp85_2085 %>%
  group_by(water_day) %>% 
  tally() %>%
  ggplot(aes(water_day, n)) + 
  geom_col(fill = "gray") +
  ylim(0, 25) +
  xlab("Water Day (1 = Oct 1") +
  ylab("Occurrences") +
  ggtitle(label = "Annual distribution of tidal maxima",
  subtitle = "Daily data, RCP 8.5, 2070-2099") +
  theme_bw() +
  ggsave(here("tdi/figures/daily/rcp85_2085_daily.png"))


combined_plot <- ggarrange(daily_hist_plot, daily_rcp45_2070_plot, daily_rcp45_2085_plot, daily_rcp85_2050_plot, daily_rcp85_2070_plot, daily_rcp85_2085_plot) +
  ggsave(here("tdi/figures/daily/combined_daily.png"))




```


## Smoothed density plots 

```{r}

daily_hist_density <- daily_hist %>%
  ggplot(aes(water_day)) + 
  geom_density() +
  xlab("Water Day (1 = Oct 1)") +
  ylab("Density") +
  ggtitle(label = "Annual distribution of TDI maxima", 
       subtitle = "Daily data, RCP 4.5 and 8.5, 1980-2009") +
  theme_bw() +
  ggsave("tdi/figures/daily/density/historical.png")

  
daily_rcp45_2070_density <- daily_rcp45_2070 %>%
  ggplot(aes(water_day)) + 
  geom_density() +
  xlab("Water Day (1 = Oct 1") +
  ylab("Density") +
  ggtitle(label = "Annual distribution of tidal maxima",
  subtitle = "Daily data, RCP 4.5, 2055-2084") +
  theme_bw() +
  ggsave("tdi/figures/daily/density/rcp45_2070_daily.png")


daily_rcp45_2085_density <- daily_rcp45_2085 %>%
  ggplot(aes(water_day)) + 
  geom_density() +
  xlab("Water Day (1 = Oct 1") +
  ylab("Density") +
  ggtitle(label = "Annual distribution of tidal maxima",
  subtitle = "Daily data, RCP 4.5, 2070-2099") +
  theme_bw() +
  ggsave("tdi/figures/daily/density/rcp45_2085_daily.png")


daily_rcp85_2050_density <- daily_rcp85_2050 %>%
  ggplot(aes(water_day)) + 
  geom_density() +
  xlab("Water Day (1 = Oct 1") +
  ylab("Density") +  
  ggtitle(label = "Annual distribution of tidal maxima",
  subtitle = "Daily data, RCP 8.5, 2035-2064") +
  theme_bw() +
  ggsave("tdi/figures/daily/density/rcp85_2050_daily.png")



daily_rcp85_2070_density <- daily_rcp85_2070 %>%
  ggplot(aes(water_day)) + 
  geom_density() +
  xlab("Water Day (1 = Oct 1") +
  ylab("Density") +
  ggtitle(label = "Annual distribution of tidal maxima",
  subtitle = "Daily data, RCP 8.5, 2055-2084") +
  theme_bw() +
  ggsave("tdi/figures/daily/density/rcp85_2070_daily.png")


daily_rcp85_2085_plot <- daily_rcp85_2085 %>%
  ggplot(aes(water_day)) + 
  geom_density() +
  xlab("Water Day (1 = Oct 1") +
  ylab("Density") +
  ggtitle(label = "Annual distribution of tidal maxima",
  subtitle = "Daily data, RCP 8.5, 2070-2099") +
  theme_bw() +
  ggsave("tdi/figures/daily/density/rcp85_2085_daily.png")


# Alternate option: bkde() in KernSmooth package
x <- daily_hist$water_day
est <- bkde(x, bandwidth=0.25)
plot(est, type="l")


# Combine smoothed curves from each time period into one plot 

daily_combined <- rbind(daily_hist, daily_rcp45_2070, daily_rcp45_2085, daily_rcp85_2050, daily_rcp85_2070, daily_rcp85_2085)

density_plot <- daily_combined %>%
  ggplot() + 
  geom_density(aes(x = water_day, group=scenario, color=scenario)) +
  geom_vline(xintercept=1, color = "gray") +
  geom_text(aes(x=1, label="Oct 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +  
  geom_vline(xintercept=32, color = "gray") +
  geom_text(aes(x=32, label="Nov 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +
  geom_vline(xintercept=62, color = "gray") +
  geom_text(aes(x=62, label="Dec 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +
  geom_vline(xintercept=93, color = "gray") +
  geom_text(aes(x=93, label="Jan 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +
  geom_vline(xintercept=124, color = "gray") +
  geom_text(aes(x=124, label="Feb 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +
  geom_vline(xintercept=152, color = "gray") +
  geom_text(aes(x=152, label="Mar 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +
  geom_vline(xintercept=183, color = "gray") +
  geom_text(aes(x=183, label="Apr 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +
  geom_vline(xintercept=213, color = "gray") +
  geom_text(aes(x=213, label="May 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +
  geom_vline(xintercept=244, color = "gray") +
  geom_text(aes(x=244, label="Jun 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +
  geom_vline(xintercept=274, color = "gray") +
  geom_text(aes(x=274, label="Jul 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +  
  geom_vline(xintercept=305, color = "gray") +
  geom_text(aes(x=305, label="Aug 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +
  geom_vline(xintercept=336, color = "gray") +
  geom_text(aes(x=336, label="Sep 1", y=0.012), colour="gray", angle=90, vjust = 1.2, text=element_text(size=6)) +
  xlab("Water Day (1 = Oct 1)") +
  ylab("Density") +
  ggtitle(label = "Annual distribution of tidal maxima",
  subtitle = "Daily data projected under one historical and five future scenarios") +
  theme_classic() +
  ggsave("tdi/figures/daily/density/combined.png")

  density_plot
  
  
  

```





