---
title: "TDI Max Analysis"
author: "Molly Williams"
date: "3/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Load packages and data

```{r}

library(tidyverse)
library(ggpubr)
library(here)


# Add column for water year and water month (Oct = 1, Nov = 2 etc.)
# Add in missing month data where necessary

may <- c(0, NA, NA, NA, 5, 1)
jun <- c(0, NA, NA, NA, 6, 1)
jul <- c(0, NA, NA, NA, 7, 1)
aug <- c(0, NA, NA, NA, 8, 1)
sep <- c(0, NA, NA, NA, 9, 1)
oct <- c(0, NA, NA, NA, 10, 1)
nov <- c(0, NA, NA, NA, 11, 1)


hist <- read_csv("tdi/tdi_historical.csv") %>%
  na.omit() %>%
  rbind(jul) %>% 
  mutate(water_year = ifelse(Month>9, Year+1, Year)) %>% 
  mutate(water_month = ifelse(Month<10, Month+3, ifelse(Month>9, Month-9, Month))) %>% 
  mutate(month_name = month.abb[Month])

hist_mean <- hist %>% 
  group_by(Year, Month, Day, water_year, water_month) %>% 
  summarise_at(vars("Flow (cfs)"), funs(mean(., na.rm=TRUE)))

rcp85_2050 <- read.csv(here("tdi/tdi_2050_RCP85.csv"),  na = c("", "NA")) %>%
  na.omit() %>% 
  rbind(jul) %>% 
  rbind(aug) %>% 
  rbind(sep) %>% 
  rbind(oct) %>% 
  mutate(water_year = ifelse(Month>9, Year+1, Year)) %>% 
  mutate(water_month = ifelse(Month<10, Month+3, ifelse(Month>9, Month-9, Month))) %>% 
  mutate(month_name = month.abb[Month])


rcp85_2085 <- read_csv(here("tdi/tdi_2085_RCP85.csv"), skip_empty_rows = TRUE) %>%
  na.omit() %>%
  rbind(may) %>% 
  rbind(jun) %>% 
  mutate(water_year = ifelse(Month>9, Year+1, Year)) %>% 
  mutate(water_month = ifelse(Month<10, Month+3, ifelse(Month>9, Month-9, Month))) %>% 
  mutate(month_name = month.abb[Month])


rcp45_2085 <- read_csv(here("tdi/tdi_2085_RCP45.csv"), skip_empty_rows = TRUE) %>%
  na.omit() %>% 
  rbind(jul) %>% 
  rbind(oct) %>% 
  rbind(nov) %>% 
  mutate(water_year = ifelse(Month>9, Year+1, Year)) %>% 
  mutate(water_month = ifelse(Month<10, Month+3, ifelse(Month>9, Month-9, Month))) %>% 
  mutate(month_name = month.abb[Month])


rcp45_2070 <- read_csv(here("tdi/tdi_2070_RCP45.csv"), skip_empty_rows = TRUE) %>%
  na.omit() %>% 
  rbind(jul) %>% 
  rbind(oct) %>% 
  mutate(water_year = ifelse(Month>9, Year+1, Year)) %>% 
  mutate(water_month = ifelse(Month<10, Month+3, ifelse(Month>9, Month-9, Month))) %>% 
  mutate(month_name = month.abb[Month])


rcp85_2070 <- read_csv(here("tdi/tdi_2070_RCP85.csv"), skip_empty_rows = TRUE) %>%
  na.omit() %>% 
  rbind(jul) %>% 
  rbind(aug) %>% 
  rbind(oct) %>% 
  mutate(water_year = ifelse(Month>9, Year+1, Year)) %>% 
  mutate(water_month = ifelse(Month<10, Month+3, ifelse(Month>9, Month-9, Month))) %>% 
  mutate(month_name = month.abb[Month])




```


*Question: Which months are most likely to contain the annual tidal maximums? Is there a trend, and does it change under different future RCP scenarios?* 



# Histograms for visualization of trend - quick look

```{r}

par(mfrow = c(2, 3))

hist(hist$water_month)

hist(rcp85_2050$water_month)

hist(rcp45_2070$water_month)

hist(rcp85_2070$water_month)

hist(rcp85_2085$water_month)

hist(rcp45_2085$water_month)



# All scenarios appear to show the same trend; distributions are not normal


```


# Proper histograms

```{r}

# Tally maxima for each month and create bar plot
# Add line of data for summer month(s) where none exist, when necessary



hist_plot <- hist %>%
  group_by(Month, water_month, month_name) %>% 
  tally() %>%
  mutate(n = ifelse(Month==7, 0, n)) %>% # set july data to 0 
  ggplot(aes(reorder(month_name, water_month), n)) + 
  geom_col(fill = "gray") +
  ylim(0, 160) +
  xlab("Month") +
  ylab("Count") +
  ggtitle("Annual TDI maxima by month - Historical, 1980-2009") +
  theme_bw() +
  ggsave(here("tdi/figures/historical.png"))

  
rcp45_2070_plot <- rcp45_2070 %>%
  group_by(Month, water_month, month_name) %>% 
  tally() %>% 
  mutate(n = ifelse(Month==7, 0, ifelse(Month==10, 0, n))) %>% # set july and october data to 0
  ggplot(aes(reorder(month_name, water_month), n)) + 
  geom_col(fill = "gray") +
  ylim(0, 110) +
  xlab("Month") +
  ylab("Count") +
  ggtitle("Annual TDI maxima by month - RCP 4.5, 2055-2084") +
  theme_bw() +
  ggsave(here("tdi/figures/rcp45_2070.png"))
  
rcp45_2085_plot <- rcp45_2085 %>%
  group_by(Month, water_month, month_name) %>% 
  tally() %>% 
  mutate(n = ifelse(Month==7, 0, ifelse(Month==10, 0, ifelse(Month==11, 0, n)))) %>% # set july, october and nov data to 0 
  ggplot(aes(reorder(month_name, water_month), n)) + 
  geom_col(fill = "gray") +
  ylim(0, 110) +
  xlab("Month") +
  ylab("Count") +
  ggtitle("Annual TDI maxima by month - RCP 4.5, 2070-2099") +
  theme_bw() +
  ggsave(here("tdi/figures/rcp45_2085.png"))

rcp85_2050_plot <- rcp85_2050 %>%
  group_by(Month, water_month, month_name) %>% 
  tally() %>% 
  mutate(n = ifelse(Month==7, 0, ifelse(Month==8, 0, ifelse(Month==9, 0, ifelse(Month==10, 0, n))))) %>% # set july, aug, sep and oct data to 0 
  ggplot(aes(reorder(month_name, water_month), n)) + 
  geom_col(fill = "gray") +
  ylim(0, 110) +
  xlab("Month") +
  ylab("Count") +
  ggtitle("Annual TDI maxima by month - RCP 8.5, 2035-2064") +
  theme_bw() +
  ggsave(here("tdi/figures/rcp85_2050.png"))
  

rcp85_2070_plot <- rcp85_2070 %>%
  group_by(Month, water_month, month_name) %>% 
  tally() %>% 
  mutate(n = ifelse(Month==7, 0, ifelse(Month==8, 0, ifelse(Month==10, 0, n)))) %>% # set july, aug and october data to 0 
  ggplot(aes(reorder(month_name, water_month), n)) + 
  geom_col(fill = "gray") +
  ylim(0, 110) +
  xlab("Month") +
  ylab("Count") +
  ggtitle("Annual TDI maxima by month - RCP 8.5, 2055-2084") +
  theme_bw() +
  ggsave(here("tdi/figures/rcp85_2070.png"))

rcp85_2085_plot <- rcp85_2085 %>%
  group_by(Month, water_month, month_name) %>% 
  tally() %>%   
  mutate(n = ifelse(Month==5, 0, ifelse(Month==6, 0, n))) %>% # set july and october data to 0 
  ggplot(aes(reorder(month_name, water_month), n)) + 
  geom_col(fill = "gray") +
  ylim(0, 110) +
  xlab("Month") +
  ylab("Count") +
  ggtitle("Annual TDI maxima by month - RCP 8.5, 2070-2099") +
  theme_bw() +
  ggsave(here("tdi/figures/rcp85_2085.png"))


combined_plot <- ggarrange(hist_plot, rcp45_2070_plot, rcp45_2085_plot, rcp85_2050_plot, rcp85_2070_plot, rcp85_2085_plot) +
  ggsave(here("tdi/figures/combined.png"))


```


# Stats 
## How likely is a random maximum flow value to be drawn from a winter month? Are the highest flow values significantly concentrated in winter months? 


```{r}

# Comparison between likelihood of drawing a sample from other seasons? 

# Mean/median doesn't necessarily make sense because can you have a mean month? 

# Bootstrapping because the distribution is not normal; replicating the samples


# Historical

set.seed(222)
bstrap <- c()

for (i in 1:1000){  # Create 1000 bootstrap samples

bsample <- sample(hist$Month,10,replace=T) # calculate the bootstrap estimate
bestimate <- mean(bsample)
bstrap <- c(bstrap,bestimate)} #lower bound


quantile(bstrap,.025)
quantile(bstrap,.975)


# RCP 8.5: 2050

bstrap <- c()

for (i in 1:1000){  # Create 1000 bootstrap samples

bsample <- sample(rcp85_2050$Month,10,replace=T) #now calculate the bootstrap estimate
bestimate <- mean(bsample)
bstrap <- c(bstrap,bestimate)} #lower bound

summary(rcp85_2050$Month)
quantile(bstrap,.025)
quantile(bstrap,.975)



# RCP 4.5: 2070

bstrap <- c()

for (i in 1:1000){  # Create 1000 bootstrap samples

bsample <- sample(rcp45_2070$Month,10,replace=T) #now calculate the bootstrap estimate
bestimate <- mean(bsample)
bstrap <- c(bstrap,bestimate)} #lower bound

summary(rcp45_2070$Month)
quantile(bstrap,.025)
quantile(bstrap,.975)



# RCP 8.5: 2070

bstrap <- c()

for (i in 1:1000){  # Create 1000 bootstrap samples

bsample <- sample(rcp85_2070$Month,10,replace=T) #now calculate the bootstrap estimate
bestimate <- mean(bsample)
bstrap <- c(bstrap,bestimate)} #lower bound

summary(rcp85_2070$Month)
quantile(bstrap,.025)
quantile(bstrap,.975)



# RCP 8.5: 2085

bstrap <- c()

for (i in 1:1000){  # Create 1000 bootstrap samples

bsample <- sample(rcp85_2085$Month,10,replace=T) #now calculate the bootstrap estimate
bestimate <- mean(bsample)
bstrap <- c(bstrap,bestimate)}

summary(rcp85_2085$Month)
quantile(bstrap,.025)
quantile(bstrap,.975)



# RCP 4.5: 2085

bstrap <- c()

for (i in 1:1000){  # Create 1000 bootstrap samples

bsample <- sample(rcp45_2085$Month,10,replace=T) #now calculate the bootstrap estimate
bestimate <- mean(bsample)
bstrap <- c(bstrap,bestimate)}

summary(rcp45_2085$Month)
quantile(bstrap,.025)
quantile(bstrap,.975)





```



